---
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, echo=F}
knitr::opts_knit$set(root.dir = '~/Dropbox/2_supervisions/Carolina Reyes-Puig/microclimates/microclimates/')
```

### To do

* Fine-tune models for each microhabitat.
* ...
* ...


# Background

This repository contains all the code and data to simulate different microclimates. 

We simulate different microclimates in Castro São Paio using NicheMapR. The weather data comes from Modivas (https://www.wunderground.com/dashboard/pws/IMODIV1). 


## Repository structure

* **/code/** 
  * **aux_functions.R**: helpful functions to handle data
    * `readLoggers`: reads and cleans datalogger data given the logger name and timeperiod. 
    * `read.logger`: reads the data from iButton csv files. Internal of `readLoggers`.
    * `clean.logger`: cleans datalogger data, and formats dates. Internal of `readLoggers`.
    * `clean.logger2`: same as `clean.logger` but for a different time format. Internal of `readLoggers`.
    * `prepare.weather`: adds logger data to the weather station data. Internal of `run.microclimate`.
    * `retrieve.output`: retrieves output of the microclimate model. Internal of `run.microclimate`.
    * `run.microclimate`: runs the model, if needed it prepares the weather data, and finally retrieves the data from the model.
    * `plot.predictions`: plot simulation predictions and datalogger observations.
    * `site.info`: get coordinates, elevation, slope and aspect for each site from the datalogger table.
  * **micro_custom.R**: Function to prepare the input for NicheMapR microclimate model and run the model.
  * **microclimate_hourly_Castro.R**: example script that shows how to use hourly data from weather stations as input for the NicheMapR microclimate model.
  * **prepare_rasters.R**: script used to compute the *slope* and *aspect* in the study area, and save the files in the *terrain* folder.
  * **prepare_weather.R**: script used to download and prepare the weather data from Modivas station, which is then saved in the *weather* folder. The script can download data from any station, if you supply its code in wunderground.
  * **read_dataLoggers.R**: example script to read and plot datalogger data (Old).
* **/dataloggers_Castro/** datalogger data on temperature and humidity.
* **/terrain/** 
  * **marrisk-2019-02-20-dsm.tif**: digital elevation model of Castro Saõ Paio.
  * **marrisk-2019-02-20-dsmshd.tif**: digital elevation model (shade).
  * **marrisk-2019-02-20-orto.tif**: ortophoto.
  * **slope.tif**: slope for the area where dataloggers where placed.
  * **aspect.tif**: aspect for the area where dataloggers where placed.
  * **orto.tif**: ortophoto cropped for the area where dataloggers where placed.
* **/weather/** weather data from Modiva station, downloaded from wunderground.
* **microclimates_CastroSampaio.Rmd**: Run simulations for different microhabitats and compare to the data recorded by iButtons placed in those microclimates.


## Study area

```{r, echo=F, warning=F, message=F}
library(terra)
# read ortophoto
ortoph <- rast('terrain/orto.tif')

# read dataloggers info
dl_coords <- read.csv(file = 'dataloggers_Castro/ibutton_coords.csv', dec=',', sep=';')
air_loggers <- which(dl_coords$codes %in% c('a1','a2','a3'))

plot(ortoph)
points(dl_coords[-air_loggers, c("longitude", "latitude")], cex=2, pch=20, col='purple')
points(dl_coords[air_loggers, c("longitude", "latitude")], cex=2, pch=20, col='gold')
```
